Modeling the Circumnuclear Mediums and Accetion Rates of Quiescent Supermassive Black Holes

### 2015-01-09 ms.tex
editing intro2

Many past studies have focused on relatively massive galaxies.  A key result of this work is the onset of , and the need for AGN feedback.  Here we instead neglect radiative cooling, focusing on time-dependent models.  This simple approach allows us to systematically and to derive simple analytic expressions that prove useful in exploring their sensitivity on.

The one-dimensional steady state flow of gas is usually characterized
by an inflow-outflow structure, with a critical radius known as the
``stagnation radius" $\rs$ where the radial velocity goes to zero.
Mass loss from stars interior to the stagnation radius is accreted,
while that outside $\rs$ is unbound in an outflow from the nucleus.
The stagnation radius, rather than the Bondi radius, is thus
ultimately responsible for setting the SMBH accretion rate, although (when it exists)
$\rs$ can in many cases lie within a factor of few of the
nominal Bondi radius.
% Furthermore, in some cases we find that no stagnation
% radius exists at all; this formally implies that the entire of ISM of
% the galaxy is feeding the SMBH, potentially resulting in much higher
% accretion rate than would be predicted by simple Bondi accretion. 
The main goal of our analysis is to provide a framework for
interpreting the properties of quiescent galactic nuclei given the
comparatively well understood physics of stellar winds and supernova
heating.

>>>>

Past studies, including multi-dimensional hydrodynamics and a variety of (parameterized) physical effects, have focused on relatively massive elliptical galaxies (Ciotti refs).  A key result of this work is the periodic development of cooling instabilities, which temporarily increase the gas accretion rate before black hole feedback grows sufficiently important to halt this growth.  Here we instead focus on time-independent models, neglecting radiative cooling.  This simple approach allows us to systematically and to derive simple analytic expressions that prove useful in exploring whether cooling instabilties are always manifest, or whether other forms of non-AGN feedback can result in steady accretion.  Even if cooling instabilties develop on galactic scales, phases of stable accretion may persist on small scales.  We are thus motivated to explore whether it steady-flow is possible under any circumstances, or whether accretion is always building towards instability.

In the presence of strong heating, one-dimensional steady-state flow is characterized by an inflow-outflow structure, with a critical radius known as the``stagnation radius" $\rs$ where the radial velocity passes through zero.  Mass loss from stars interior to the stagnation radius is accreted, while that outside $\rs$ is unbound in an outflow from the nucleus.  The stagnation radius, rather than the Bondi radius, thus controls the SMBH accretion rate, although $\rs$ can in many cases lie within a factor of few of the nominal Bondi radius.  In the case of weak heating, however, no stagnation radius may exist at all, i.e. the entire ISM of the galaxy is feeding the SMBH.  Another goal of this work is to assess under what conditions a stagnation radius exists, as this question is intimately tied to the one of cooling instability.  
% Furthermore, in some cases we find that no stagnation
% radius exists at all; this formally implies that the entire of ISM of
% the galaxy is feeding the SMBH, potentially resulting in much higher
% accretion rate than would be predicted by simple Bondi accretion. 
The main goal of our analysis is to provide a framework for
interpreting the properties of quiescent galactic nuclei given the
comparatively well understood physics of stellar winds and supernova
heating.
